Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-05 draft.tex
additional references
yet more preferences
a rouugh and messy introduction

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
%\author{}
%\author{Paolo Viappiani} \affil{LIP6\\\email{paolo.viappiani@lip6.fr}}
%\author{Olivier Cailloux} 
%\author{Stefano Moretti}%\affil{LAMSADE}
%\author{Beatrice Napolitano}\affil{LAMSADE}

@@

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item Structure of the paper
\end{itemize}

@@

@@

%The voting scheme selects the winner (a consensus option).
%Incremental elicitation 
% The paper is organized as follows.

@@

\section{Background}

We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.

@@

\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}

@@

Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
Obviously we have 
\[ s(x; \profile, \w) = \sum_{j=1}^n s(x; v_j,\w). \]

@@

\section{Interactive Elicitation}

@@

\section{Empirical Evaluation}

@@

% Conclusions
% summary of contribution, more comments, future works.

%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}

>>>>

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences}
%\author{}
\author{Olivier Cailloux \and Stefano Moretti \and Beatrice Napolitano \and Paolo Viappiani} %\affil{LIP6\\\email{paolo.viappiani@lip6.fr}
%\author{Olivier Cailloux} 
%\author{Stefano Moretti}%\affil{LAMSADE}
%\author{Beatrice Napolitano}\affil{LAMSADE}

@@

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item Structure of the paper
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}
\end{itemize}

@@

The traditional approach to social choice assumes that both the social function and the full preference orderings of the voters are expressed beforehand. 
As noted by several authors requiring voters to express full preference orderings can be onerous (especially for large sets of alternatives)

% Given partial information about voter preferences, how does one choose a suitable approximate winner? 
Scoring rules are a particularly common methods used to aggregate rankings and determine  a winner.
The score can be seen as a utility for the society...

%and often captures more information than is needed to determine the winner
We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

%which queries to ask of which voters. 
We discuss  heuristics that allow us to determine queries that quickly allow one to reduce minimax regret.

 Our experimental results on randomly generated and real world data sets show...

@@

%The voting scheme selects the winner (a consensus option).
%Incremental elicitation 
\medskip
The paper is organized as follows.
In Section \ref{sec:background} we provide the necessary background.
We introduce the minimax criterion and in Section \ref{sec:mmr}.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minima regret; finally in Section 
\ref{sec:conclusions} we provide some final thoughts.

@@

\section{Background}\label{sec:background}

We introduce the basic concepts.
We assume that there is a set $A$ of $m$ alternatives (for instance products, restaurants, movies, public projects, job candidates, etc.) and $n$ agents (voters); each agent is associated to a preference order.
The goal of the voters is to make a consensus choice, that is to select a ``winner'' given voter rankings.

@@

\section[Minimax regret under partial profile and weight information]{Minimax regret under partial profile and weight \\ information}
\label{sec:mmr}

@@

Scoring rules are additively decomposable.
Let $s(x; v_j,\w)=w_{v_j(x)}$ be the number of points that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}), that is the weight of position $v_j(x)$.
Obviously we have 
\[ s(x; \profile, \w) = \sum_{j=1}^n s(x; v_j,\w). \]

@@

\section{Interactive Elicitation} \label{sec:elicit}

@@

\section{Empirical Evaluation} \label{sec:experiments}

@@

\section{Conclusions}  \label{sec:conclusions}
%  Possible future works: manipulation,

This is an awesome paper, it should be accepted right away and win a prize.

% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}
